Untitled

### 2025-02-21 code/manuscript_altanalysis.Rmd
final code updates

@@

@@

table(table(dfc$`BHCMIS ID`))

dfc %>% filter(ID.x == "90")

dfc %>% 
  filter(`BHCMIS ID` == "012070")

@@

@@

@@

@@

@@

@@

plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, linetype = CompetitorsInArea)) + ylab("FQHCs") + 
  #geom_point(size = 1.1) + 
  geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
  #geom_dl(label=c(rep("0 Rivals", length(unique(p$Year))), rep("1 Rival", length(unique(p$Year))), rep("2 Rivals", length(unique(p$Year))), rep("3+ Rivals", length(unique(p$Year)))), 
   #       method = list("last.points", hjust = 1, vjust = c(-3, 2, 2.5, -1), cex = 1.5), inherit.aes=T ) + 
  #guides(linetype = "none") + 
  guides(linetype = guide_legend(title = "# other CHCs\nin Incumbent's\nService Area")) + 
  scale_linetype_manual(values=c(1,2,3, 4)) + 
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))

plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
            group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
  ungroup() %>% 
  group_by(Year, Counts) %>% 
  summarise(Zips = n()) %>% 
  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
  group_by(Counts.f, Year) %>% 
  summarise(Zips = sum(Zips)) %>% 
  #filter(Year >= 2010) %>% 
  ggplot(aes(x = Year, y = Zips, group = Counts.f, linetype = Counts.f)) + 
  #geom_point(size = 1.1) + 
  geom_line(size = 1.1) + theme_tufte_revised() + 
  ggtitle("Zip Codes by Number of FQHC Sites") + 
  #geom_dl(label=c(rep("1 Site", length(unique(p$Year))), rep("2+ Sites", length(unique(p$Year)))), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
  #guides(linetype = "none") + 
  ylim(0, 4000) +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold")) + 
  scale_linetype_manual(values=c(5, 6)) + 
  guides(linetype = guide_legend(title = "# CHC Sites by\nZip Code"))

@@

p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2023", face = "bold", size = 14))

@@

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  #model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
  #coeffs <- rbind(coeffs, model$coeftable[2,])
  model <- feols(Outcome ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year | I((10000 - ClinicHHI)/1000) ~ Tx*value, cluster = "ID", data = df.temptemptemp)
  coeffs <- rbind(coeffs, model$coeftable[1,])

@@

    event_study(data = df.temptemp,
  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
  filter(abs(term) <= 6) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

  filter(Measure %in% c('Total','Staff','Altman','Pct.MCD','Pct.None','Complexity')) %>% 
  mutate(Group = ifelse(Measure %in% c('Total','Staff','logPatsPerStaff','Qcomp'), "Operational Metrics", 
                        ifelse(Measure %in% c('Altman','LiabPctAssets','months_of_cash'), 'Financial Metrics', 'Selection Metrics'))) %>% 
  rename(Year = term) %>% 
  ggplot(aes(x = Year, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + 
  facet_wrap(Group~Measure, scales = "free_y", ncol = 2)

@@

   model <-  did2s(
      data = df.temptemptemp,
      yname = "Outcome",
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>=2, 1, 0), ref = FALSE),
        #second_stage =~ i(Tx, ref = FALSE) + I(as.numeric(Tx) * as.numeric(value_min)) ,
        cluster_var = "ID",
      verbose = TRUE
    )

@@

>>>>

length(unique(uds.covariates$BHCMISID))

@@

length(unique(df.comp[df.comp$Year %in% included.years,]$BHCMISID))

df.comp %>% 
    filter(Year == 2022) %>% 
    mutate(Missing = ifelse(is.na(ngla_net_gain_loss), "Missing", "Have")) %>% 
    ungroup() %>% 
    select(Missing, Total, Pct.NHA:Pct.COM) %>% 
    #filter(!complete.cases(.)) %>% 
    tbl_summary(by = Missing, 
                  statistic = list(all_continuous() ~ "{mean} ({sd})"),
  missing = "no", digits = list(everything() ~ c(2))) %>% 
    add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))

@@

# table(table(dfc$`BHCMIS ID`))
# 
# 
# 
# dfc %>% filter(ID.x == "90")
# 
# dfc %>% 
#   filter(`BHCMIS ID` == "012070")

length(unique(dfc$`BHCMIS ID`))

@@

length(unique(dfc$`BHCMIS ID`))

@@

length(unique(df.mt$`BHCMIS ID`))

@@

length(unique(df.temptemp$`BHCMIS ID`))

@@

summary(df.temptemp[df.temptemp$Year == 2022 & df.temptemp$Closed == 0,])

df.temptemp[df.temptemp$Closed == 0,]

# 
# fullfins <- ufins2 %>%
#   mutate(months_of_cash = as.numeric(months_of_cash),
#                ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
#                quick_ratio = as.numeric(quick_ratio),
#                Liquidity = (Assets - Liabilities) / Assets,
#                Profitability = ngla_revenue / ngla_expense * 100, #Assets,
#                Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
#                NetWorth = (Assets - Liabilities) / Liabilities,
#             Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense,
#             LiabPctAssets = Liabilities / Assets * 100,
#             Eff = ngla_prog_serv_revenue / Assets,
#             LiabPctRev = ngla_prog_serv_revenue / ngla_expense) %>%
#   mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity),
#          Profitability = ifelse(is.infinite(Profitability), NA, Profitability),
#          Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency),
#          NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth),
#          Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>%
#   select(BHCMIS.ID, form_year, Altman, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, ngla_net_gain_loss )
# 
# 
# 
# 
# df.temptemp <- df.temptemp %>%
#   left_join(fullfins %>% unique(), by = c("BHCMIS ID" = "BHCMIS.ID","Year" = "form_year")) %>%
#   unique() %>%
#   mutate(Altman.x = ifelse(is.na(Altman.x), Altman.y, Altman.x),
#          quick_ratio.x = ifelse(is.na(quick_ratio.x), quick_ratio.y, quick_ratio.x),
#          months_of_cash.x = ifelse(is.na(months_of_cash.x), months_of_cash.y, months_of_cash.x),
#          Profitability.x = ifelse(is.na(Profitability.x), Profitability.y, Profitability.x),
#          LiabPctAssets.x = ifelse(is.na(LiabPctAssets.x), LiabPctAssets.y, LiabPctAssets.x),
#          Staff.x = ifelse(is.na(Staff.x), Staff.y, Staff.x),
#          ngla_net_gain_loss.x = ifelse(is.na(ngla_net_gain_loss.x), ngla_net_gain_loss.y, ngla_net_gain_loss.x)) %>%
#   rename(Altman = Altman.x,
#          quick_ratio = quick_ratio.x,
#          months_of_cash = months_of_cash.x,
#          Profitability = Profitability.x,
#          LiabPctAssets = LiabPctAssets.x,
#          Staff = Staff.x,
#          ngla_net_gain_loss = ngla_net_gain_loss.x) %>%
#   unique()

df.temptemp %>% 
  filter(Year == 2022) %>% 
  mutate(Missing = ifelse(is.na(Qcomp), "Missing", "Have")) %>% 
  select(Missing, Total, Pct.NHA:Staff) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Missing, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"),
missing = "no", digits = list(everything() ~ c(2))) %>% 
  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))

df.temptemp %>% 
  filter(Year == 2022) %>% 
  mutate(Missing = ifelse(is.na(Altman), "Missing", "Have")) %>% 
  select(Missing, Total, Pct.NHA:Staff) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Missing, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"),
missing = "no", digits = list(everything() ~ c(2))) %>% 
  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))

@@

## Balance by 990 vs non990 data CHCs
```{r}

df.temptemp %>% 
  filter(Year == 2010) %>% 
  mutate(Missing = ifelse(is.na(Altman), "Missing", "Have")) %>% 
  select(Missing, Total, Pct.NHA:Staff) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Missing, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"),
missing = "no", digits = list(everything() ~ c(2))) %>% 
  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))

fullfins <- ufins2 %>%
  mutate(months_of_cash = as.numeric(months_of_cash),
               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_revenue / ngla_expense * 100, #Assets,
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities,
            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense,
            LiabPctAssets = Liabilities / Assets * 100,
            Eff = ngla_prog_serv_revenue / Assets,
            LiabPctRev = ngla_prog_serv_revenue / ngla_expense) %>%
  mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity),
         Profitability = ifelse(is.infinite(Profitability), NA, Profitability),
         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency),
         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth),
         Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>%
  select(BHCMIS.ID, form_year, Altman, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, ngla_net_gain_loss )

df.temptemp <- df.temptemp %>%
  left_join(fullfins %>% unique() %>%
  filter(!(`BHCMIS.ID` == "03E00494" & form_year == 2010) & 
           !(`BHCMIS.ID` == "03E01039" & form_year ==	2015)& 
           !(`BHCMIS.ID` == "05E00445" & form_year ==	2015)& 
           !(`BHCMIS.ID` == "05E00499" & form_year ==	2013)&

           !(`BHCMIS.ID` == "06E00500" & form_year ==	2016)& 
           !(`BHCMIS.ID` == "07E00486" & form_year ==	2014)& 
           !(`BHCMIS.ID` == "07E00514" & form_year ==	2014)& 
           !(`BHCMIS.ID` == "10E00136" & form_year ==	2013)), by = c("BHCMIS ID" = "BHCMIS.ID","Year" = "form_year"))  %>% 
  unique() %>%
  mutate(Altman.x = ifelse(is.na(Altman.x), Altman.y, Altman.x),
         quick_ratio.x = ifelse(is.na(quick_ratio.x), quick_ratio.y, quick_ratio.x),
         months_of_cash.x = ifelse(is.na(months_of_cash.x), months_of_cash.y, months_of_cash.x),
         Profitability.x = ifelse(is.na(Profitability.x), Profitability.y, Profitability.x),
         LiabPctAssets.x = ifelse(is.na(LiabPctAssets.x), LiabPctAssets.y, LiabPctAssets.x),
         Staff.x = ifelse(is.na(Staff.x), Staff.y, Staff.x),
         ngla_net_gain_loss.x = ifelse(is.na(ngla_net_gain_loss.x), ngla_net_gain_loss.y, ngla_net_gain_loss.x)) %>%
  rename(Altman = Altman.x,
         quick_ratio = quick_ratio.x,
         months_of_cash = months_of_cash.x,
         Profitability = Profitability.x,
         LiabPctAssets = LiabPctAssets.x,
         Staff = Staff.x,
         ngla_net_gain_loss = ngla_net_gain_loss.x) %>%
  unique()

df.temptemp %>% 
  filter(Year == 2010) %>% 
  select(Altman, Pct.NHA:Pct.Homeless, Pct.MCD:Pct.None) %>% 
  mutate(Missing = ifelse(is.na(Altman), "Missing", "Have")) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Missing, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"),
missing = "no", digits = list(everything() ~ c(2))) %>% 
  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))

# 
# fullfins %>% 
#     filter(`BHCMIS.ID` %in% names(table(df.temptemp$`BHCMIS ID`)[table(df.temptemp$`BHCMIS ID`) != 15]))
# 
# df.temptemp %>% 
#   filter(`BHCMIS ID` %in% names(table(df.temptemp$`BHCMIS ID`)[table(df.temptemp$`BHCMIS ID`) != 15]))

```{r}
uds.6b.2022 %>% 
  filter(BHCMISID == "01E01088")

uds.quality.6b %>% 
  filter(BHCMISID == "01E01088")

df.temptemp %>% 
  filter(`BHCMIS ID` == "01E01088")
```

@@

plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, linetype = CompetitorsInArea)) + ylab("CHCs") + 
  #geom_point(size = 1.1) + 
  geom_line(size = 1.1)  + theme_tufte_revised() + ggtitle("CHCs by Number of Colocated CHCs") + 
  #geom_dl(label=c(rep("0 Rivals", length(unique(p$Year))), rep("1 Rival", length(unique(p$Year))), rep("2 Rivals", length(unique(p$Year))), rep("3+ Rivals", length(unique(p$Year)))), 
   #       method = list("last.points", hjust = 1, vjust = c(-3, 2, 2.5, -1), cex = 1.5), inherit.aes=T ) + 
  #guides(linetype = "none") + 
  guides(linetype = guide_legend(title = "# other CHCs\nin Incumbent's\nService Area")) + 
  scale_linetype_manual(values=c(1,2,3, 4)) + 
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))

plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
            group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
  ungroup() %>% 
  group_by(Year, Counts) %>% 
  summarise(Zips = n()) %>% 
  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
  group_by(Counts.f, Year) %>% 
  summarise(Zips = sum(Zips)) %>% 
  #filter(Year >= 2010) %>% 
  ggplot(aes(x = Year, y = Zips)) + 
  #geom_point(size = 1.1) + 
  geom_line(size = 1.1, aes(linetype = Counts.f)) + theme_tufte_revised() +
  ggtitle("Zip Codes by Number of CHC Sites") + 
  #geom_dl(label=c(rep("1 Site", length(unique(p$Year))), rep("2+ Sites", length(unique(p$Year)))), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
  #guides(linetype = "none") + 
  ylim(0, 4000) +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold")) + 
  scale_linetype_manual(values=c(7, 8)) + 
  guides(linetype = guide_legend(title = "# CHC Sites by\nZip Code"))

@@

p.desc <- annotate_figure(p.desc, top = text_grob("CHC Growth and Density by Zip and Clinic, UDS 1996 to 2023", face = "bold", size = 14))

@@

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  #model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
  #coeffs <- rbind(coeffs, model$coeftable[2,])
  model <- feols(Outcome ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless  | ID + Year | I((10000 - ClinicHHI)/1000) ~ Tx, cluster = "ID", data = df.temptemptemp)
  coeffs <- rbind(coeffs, model$coeftable[1,])

@@

    event_study(data = df.temptemp,
  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 6) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

  filter(Measure %in% c('Total','Staff','Altman','Pct.MCD','Pct.None','Complexity')) %>% 
  mutate(Group = ifelse(Measure %in% c('Total','Staff','logPatsPerStaff','Qcomp'), "Operational Metrics", 
                        ifelse(Measure %in% c('Altman','LiabPctAssets','months_of_cash'), 'Financial Metrics', 'Selection Metrics'))) %>% 
  mutate(Measure = ifelse(Measure == "Altman", "Financial resilience, Altman’s Z Score", 
                   ifelse(Measure == "Staff", "CHC Staff, No.",
                   ifelse(Measure == "Total", "Total Patients Served, No.", 
                   ifelse(Measure == "Complexity", "Average prevalence of select chronic conditions, %", 
                   ifelse(Measure == "Pct.MCD", "Payer Mix - % Medicaid", 
                   ifelse(Measure == "Pct.None", "Payer Mix - % Uninsured", Measure))))))) %>%
  rename(Year = term) %>% 
  ggplot(aes(x = Year, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + 
  facet_wrap(Group~Measure, scales = "free_y", ncol = 2)

@@

   model <-  did2s(
      data = df.temptemptemp,
      yname = "Outcome",
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>=2, 1, 0), ref = FALSE),
        #second_stage =~ i(Tx, ref = FALSE) + I(as.numeric(Tx) * as.numeric(value_min)) ,
        cluster_var = "ID",
      verbose = TRUE
    )

@@

## Evaluating Missingness

coeffs.did.missingButBaseline <- c(0,0,0,0)

for (k in 1:22){

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) %>% select(ClinicHHI:ACA, Treat:year.rel) %>% ungroup() %>% # filter(!is.na(Altman)) 
    inner_join(df.temptemp %>% filter(Year == 2010) %>% ungroup() %>% mutate(Missing = ifelse(is.na(Altman), "Missing", "Have")) %>% select(`BHCMIS ID`, Missing), by = c("BHCMIS ID")) %>% filter(Missing == "Have") %>% 
    filter(!complete.cases(.)) 
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

  coeffs.did.missingButBaseline <- rbind(coeffs.did.missingButBaseline, model$coeftable[1,])

core.did.estimates.missingBugBaseline <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.missingButBaseline[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, Pr...t..)

nrow(df.temptemptemp)

coeffs.did.notmissing <- c(0,0,0,0)

for (k in 1:22){

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) %>% select(ClinicHHI:ACA, Treat:year.rel) %>% ungroup() %>% # filter(!is.na(Altman)) 
    inner_join(df.temptemp %>% filter(Year == 2010) %>% ungroup() %>% mutate(Missing = ifelse(is.na(Altman), "Missing", "Have")) %>% select(`BHCMIS ID`, Missing), by = c("BHCMIS ID")) %>% filter(Missing == "Have") %>% 
    filter(complete.cases(.))

  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))

 if (sum(is.na(df.temptemptemp$Outcome)) > 2500) {
   coeffs.did.notmissing <- rbind(coeffs.did.notmissing, c(NA, NA, NA, NA))

 } else {
   model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

  coeffs.did.notmissing <- rbind(coeffs.did.notmissing, model$coeftable[1,])

core.did.estimates.notmissing <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.notmissing[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, Pr...t..)

nrow(df.temptemptemp)

coeffs.did.missing <- c(0,0,0,0)

for (k in 1:22){

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) %>% select(ClinicHHI:ACA, Treat:year.rel) %>% ungroup() %>% # filter(!is.na(Altman)) 
    inner_join(df.temptemp %>% filter(Year == 2010) %>% ungroup() %>% mutate(Missing = ifelse(is.na(Altman), "Missing", "Have")) %>% select(`BHCMIS ID`, Missing), by = c("BHCMIS ID")) %>% filter(Missing == "Missing")
